### 2023-12-15 latex/Plusone_configs/paper.tex
MLP 调参

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

@@

\subsubsection*{walking forward procedure}

\subsubsection*{Evaluation metrics : statistical & economic}

@@

\subsection*{analysis results}

@@

>>>>

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{booktabs}
\usepackage{rotating}
% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

% Place tables after the first paragraph in which they are cited.
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{all result}
% \begin{sidewaystable}
\begin{tabular}{llrrrrp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
\toprule
    &               &     IC &   ICIR &  Rank IC &  Rank ICIR &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
model & dataset &        &        &          &            &                          &                          &                               &                               \\
\midrule
ALSTM & Derivations &  0.040 &  0.066 &    0.027 &      0.048 &                   -0.002 &                   -0.016 &                         0.033 &                         0.174 \\
    & Simple &  0.005 &  0.007 &   -0.005 &     -0.008 &                    0.057 &                    0.803 &                         0.051 &                         0.258 \\
    & TermStructure &  0.029 &  0.042 &    0.026 &      0.041 &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
\midrule
GRU & Derivations &  0.021 &  0.035 &    0.017 &      0.031 &                    0.049 &                    0.310 &                         0.096 &                         0.641 \\
    & Simple & -0.023 & -0.033 &   -0.026 &     -0.040 &                    0.045 &                    0.517 &                         0.059 &                         0.310 \\
    & TermStructure &  0.004 &  0.006 &    0.002 &      0.004 &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
\midrule
LGB & Derivations &  0.019 &  0.059 &    0.085 &      0.127 &                    0.020 &                    0.264 &                        -0.085 &                        -0.355 \\
    & Simple & -0.024 & -0.050 &   -0.044 &     -0.069 &                   -0.004 &                   -0.044 &                        -0.121 &                        -0.511 \\
    & TermStructure &  0.035 &  0.066 &    0.054 &      0.079 &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
\midrule
LSTM & Derivations &  0.040 &  0.067 &    0.036 &      0.064 &                    0.047 &                    0.416 &                         0.020 &                         0.123 \\
    & Simple & -0.015 & -0.022 &   -0.026 &     -0.042 &                    0.030 &                    0.388 &                         0.044 &                         0.262 \\
    & TermStructure &  0.021 &  0.031 &    0.016 &      0.026 &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
\midrule
Linear & Derivations &  0.095 &  0.147 &    0.079 &      0.140 &                    0.165 &                    1.049 &                         0.117 &                         0.646 \\
    & Simple &  0.090 &  0.147 &    0.070 &      0.131 &                    0.068 &                    1.325 &                         0.186 &                         0.992 \\
    & TermStructure &  0.114 &  0.162 &    0.091 &      0.152 &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
\midrule
MLP & Derivations & -0.011 & -0.018 &   -0.013 &     -0.024 &                   -0.023 &                   -0.074 &                         0.056 &                         0.325 \\
    & Simple & -0.002 & -0.004 &   -0.001 &     -0.001 &                    0.195 &                    0.630 &                        -0.009 &                        -0.046 \\
    & TermStructure &  0.011 &  0.017 &    0.012 &      0.020 &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
\midrule
XGB & Derivations &  0.008 &  0.012 &    0.011 &      0.019 &                    0.062 &                    0.250 &                         0.024 &                         0.141 \\
    & Simple &  0.015 &  0.023 &    0.003 &      0.005 &                   -0.019 &                   -0.073 &                         0.042 &                         0.260 \\
    & TermStructure &  0.047 &  0.071 &    0.043 &      0.069 &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
\bottomrule

\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}

@@

\subsubsection*{walking forward procedure}
\begin{algorithm}
        \caption{walking forward procedure}
        \begin{algorithmic}
            \STATE $rollingtasks \gets Algorithm TaskRollGen\ref{Task_Roll_Gen}$
            \FOR{$task \gets rollingtasks$}
            \STATE $model \xleftarrow{fit} task[train]$
            \STATE $pred \xleftarrow{predict} task[test]$
            \STATE $preds \xleftarrow{append} pred$
            \ENDFOR
            \STATE $PRED \xleftarrow{concat} preds \text{\quad \# PRED is a time series cover Task[test]'s horizon}$
            \STATE $metrics \xleftarrow{calculate} PRED$
            \STATE $backtestingresult \gets PRED, strategy \text{\quad \# bar by bar}$
        \end{algorithmic}
\end{algorithm}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\caption{Task Roll Gen}
	\label{Task_Roll_Gen}
	\begin{algorithmic}
    	\REQUIRE TASK contains \{TRAIN, VALID, TEST, roll\_lenth\}
            \ENSURE rollingtasks with their own \{train, valid, test\}
            \STATE $fragments \gets$ Test divided by roll\_lenth
            \FOR{$m \gets fragments$}
            \STATE $task \gets Task$
            \STATE $task[test] \gets m$
            \STATE $task[valid] \gets [start\_date_{test} - 1 - lenth_{Valid}, start\_date_{test} - 1]$
            \STATE $task[train] \gets [start\_date_{TRAIN}, strat\_date_{valid} - 1]$ \text{\quad \# expanding}
            \STATE $rollingtasks \xleftarrow{append} task$
            \ENDFOR
	\end{algorithmic}
\end{algorithm}
\subsubsection*{Evaluation metrics : statistical \& economic}

@@

\subsection*{Analysis Results}
\subsubsection*{Dataset Contains Term Structure Infomation Stand Out}
In our experiment, we explore three distinct datasets named Simple, TermStructure, Derivations as before, our results show that TermStructure and Derivations with term structure infomation stand out.
\\Table~\ref{Best Dataset} select the best dataset for all models on our main metrics: IC, rank IC, information ratio of long short strategy, information ratio of constrined mean-variance optimization strategy.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Best Dataset}
\label{Best Dataset}
% \begin{sidewaystable}
\begin{tabular}{lllll}
\toprule
{} &             IC &        Rank IC & C-MVO Information Ratio & Long Short Information Ratio \\
model  &                &                &                         &                              \\
\midrule
ALSTM  &    Derivations &    Derivations &                  Simple &                TermStructure \\
GRU    &    Derivations &    Derivations &                  Simple &                  Derivations \\
LGB    &  TermStructure &    Derivations &           TermStructure &                  Derivations \\
LSTM   &    Derivations &    Derivations &           TermStructure &                       Simple \\
Linear &  TermStructure &  TermStructure &           TermStructure &                TermStructure \\
MLP    &  TermStructure &  TermStructure &                  Simple &                  Derivations \\
XGB    &  TermStructure &  TermStructure &             Derivations &                TermStructure \\
\bottomrule
\end{tabular}

\begin{flushleft} The best dataset in all models on main metircs: IC, Rank IC, C-MVO Information Ratio, Long Short Information Ratio.
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}

\end{table}
Data shows Simple dataset doesn't prevail in any model on prediction metrics, the best dataset on backtest metric also main distribute on Term Structure and Derivations. TermStructure is the best dataset at 46\% of the time while Derivations prevail at 39\% of the time.
\\As described before, TermStructure mainly extent term structure features like $\mu$ and $\Delta roll$, Derivations extent time series distribution features like rolling-ma and z-score on TermStructure features. Term structure features do improve the result, but time series distribution features don't improve obviously.
\\We will only discuss TermStructure below.

\subsubsection*{}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Statistic Metric}
% \begin{sidewaystable}
\begin{tabular}{lrrrr}
\toprule
{} &     IC &   ICIR &  Rank IC &  Rank ICIR \\
model  &        &        &          &            \\
\midrule
ALSTM  &  0.029 &  0.042 &    0.026 &      0.041 \\
GRU    &  0.004 &  0.006 &    0.002 &      0.004 \\
LGB    &  0.035 &  0.066 &    0.054 &      0.079 \\
LSTM   &  0.021 &  0.031 &    0.016 &      0.026 \\
Linear &  0.114 &  0.162 &    0.091 &      0.152 \\
MLP    &  0.011 &  0.017 &    0.012 &      0.020 \\
XGB    &  0.047 &  0.071 &    0.043 &      0.069 \\
mean   &  0.037 &  0.056 &    0.035 &      0.056 \\
\bottomrule
\end{tabular}

\begin{flushleft}
Table notes: performance of statistic metric
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Statistic Metric}
% \begin{sidewaystable}
\begin{tabular}{lp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
\toprule
{} &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
model  &                          &                          &                               &                               \\
\midrule
ALSTM  &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
GRU    &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
LGB    &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
LSTM   &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
MLP    &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
XGB    &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
mean   &                    0.051 &                    0.623 &                         0.074 &                         0.404 \\
\bottomrule
\end{tabular}

\begin{flushleft}
Table notes: performance of backtest metric
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}

\subsubsection*{Models Contrast}

@@

\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{Backtest Metric}
% \begin{sidewaystable}
\begin{tabular}{llp{2cm}p{2cm}p{2cm}p{2cm}p{2cm}p{2cm}}
\toprule
    &               &  C-MVO Annualized Return &  C-MVO Information Ratio &  C-MVO Max Drawdown &  Long Short Max Drawdown &  Long Short Annualized Return &  Long Short Information Ratio \\
model & dataset &                          &                          &                     &                          &                               &                               \\
\midrule
ALSTM & Simple &                 0.057287 &                 0.802599 &           -0.202557 &                -0.370155 &                      0.051089 &                      0.258037 \\
    & Statistical Derivations &                -0.001859 &                -0.016439 &           -0.381626 &                -0.392643 &                      0.032920 &                      0.174392 \\
    & TermStructure &                 0.070618 &                 0.743925 &           -0.202290 &                -0.452147 &                      0.111682 &                      0.578975 \\
GRU & Simple &                 0.045304 &                 0.517254 &           -0.232781 &                -0.634396 &                      0.058965 &                      0.310354 \\
    & Statistical Derivations &                 0.049236 &                 0.310389 &           -0.632122 &                -0.304792 &                      0.096182 &                      0.640611 \\
    & TermStructure &                 0.027837 &                 0.241176 &           -0.383124 &                -0.446989 &                      0.079937 &                      0.409258 \\
LGB & Simple &                -0.003863 &                -0.043739 &           -0.218599 &                -1.779844 &                     -0.121349 &                     -0.511463 \\
    & Statistical Derivations &                 0.019886 &                 0.263737 &           -0.194941 &                -1.374026 &                     -0.084887 &                     -0.354627 \\
    & TermStructure &                 0.023292 &                 0.327154 &           -0.166017 &                -1.346228 &                     -0.084790 &                     -0.367168 \\
LSTM & Simple &                 0.029657 &                 0.388443 &           -0.238059 &                -0.367246 &                      0.044252 &                      0.262347 \\
    & Statistical Derivations &                 0.047028 &                 0.416228 &           -0.228143 &                -0.535382 &                      0.019771 &                      0.122704 \\
    & TermStructure &                 0.058512 &                 0.671485 &           -0.270701 &                -0.423780 &                      0.033785 &                      0.167775 \\
Linear & Simple &                 0.068256 &                 1.324847 &           -0.107284 &                -0.182701 &                      0.186216 &                      0.992174 \\
    & Statistical Derivations &                 0.164652 &                 1.048583 &           -0.473651 &                -0.375987 &                      0.117332 &                      0.645722 \\
    & TermStructure &                 0.150301 &                 2.291034 &           -0.085517 &                -0.202081 &                      0.214001 &                      1.105489 \\
MLP & Simple &                 0.194595 &                 0.629803 &           -0.661026 &                -0.919978 &                     -0.008624 &                     -0.045972 \\
    & Statistical Derivations &                -0.023281 &                -0.073628 &           -1.500128 &                -0.803446 &                      0.055949 &                      0.324753 \\
    & TermStructure &                 0.012887 &                 0.043224 &           -1.247869 &                -0.404693 &                      0.049920 &                      0.302452 \\
SFM & Simple &                 0.055921 &                 0.265086 &           -0.607000 &                -0.592480 &                      0.043182 &                      0.215211 \\
    & Statistical Derivations &                -0.005174 &                -0.021433 &           -0.652835 &                -0.680252 &                      0.033137 &                      0.179453 \\
    & TermStructure &                -0.024066 &                -0.108211 &           -1.000576 &                -1.069861 &                     -0.017675 &                     -0.090425 \\
XGB & Simple &                -0.019219 &                -0.072545 &           -1.143294 &                -0.731367 &                      0.042195 &                      0.259511 \\
    & Statistical Derivations &                 0.062245 &                 0.249836 &           -0.953685 &                -0.477849 &                      0.023661 &                      0.141244 \\
    & TermStructure &                 0.011343 &                 0.044457 &           -1.282061 &                -0.419102 &                      0.115907 &                      0.631908 \\
\bottomrule

\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}
